### 2017-08-30 Paper01_EnthalpyAndCrystallization.tex
Method - Master Alloy - correct rod and target thickness values

\subsection{Master alloy}
The master alloy of \MgZnCa~ was produced using high-purity elements of Mg (99.85 wt\%), Zn (99.995 wt\%), and Ca (99.8 wt\%). The alloy was prepared with an in-house induction melting furnace within boron nitride coated graphite crucibles, purged with Ar (99.997 vol.\% purity) five times, and protected with a circulating Ar atmosphere. Alloy homogeneity was ensured by heating and cooling through a cycle of 700\degree C, 385\degree C, 650\degree C, 385\degree C, 650\degree C to a casting temperature of 500 \degree C and 450\degree C for injection and gravity casting respectively. Bulk amorphous \MgZnCa~ rods of nominal $2.5 mm$ diameter sectioned to \hl{2mm} thickness, and plates of nominal $1.2 mm$ thickness were produced by copper mold injection casting. The $25.4 mm$ diameter targets were prepared from cylindrical copper mold gravity castings sectioned to nominal thicknesses of \hl{3.25} $mm$, and polished. All samples and targets were stored under Ar when not being examined or used.

>>>>

\subsection{Master alloy}
The master alloy of \MgZnCa~ was produced using high-purity elements of Mg (99.85 wt\%), Zn (99.995 wt\%), and Ca (99.8 wt\%). The alloy was prepared with an in-house induction melting furnace within boron nitride coated graphite crucibles, purged with Ar (99.997 vol.\% purity) five times, and protected with a circulating Ar atmosphere. Alloy homogeneity was ensured by heating and cooling through a cycle of 700\degree C, 385\degree C, 650\degree C, 385\degree C, 650\degree C to a casting temperature of 500 \degree C and 450\degree C for injection and gravity casting respectively. Bulk amorphous \MgZnCa~ rods of nominal $2.5 mm$ diameter sectioned to $1mm$ thickness, and plates of nominal $1.2 mm$ thickness were produced by copper mold injection casting. The $25.4 mm$ diameter targets were prepared from cylindrical copper mold gravity castings sectioned to nominal thicknesses of $3.25mm$, and polished. All samples and targets were stored under Ar when not being examined or used.
